From Reversible Programs to \\ Univalent Universes and Back

### 2021-09-06 Pi/paper/reversible1.tex

For combinators, we show explcitly how values reduce along each combinator, similar to a big-step operational
semantics~\cite{chenComputationalInterpretationCompact2021,theseus}.

>>>>

For combinators, we show explicitly how values reduce along each combinator, similar to a big-step operational
semantics~\cite{chenComputationalInterpretationCompact2021,theseus}.
